---
title: "Getting Started with rgrind"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with rgrind}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(rgrind.storage_dir = tempfile("vignette_"))
dir.create(getOption("rgrind.storage_dir"))
```

## What is rgrind?

`rgrind` is a package that lets you practice R by solving small
coding puzzles, right inside your own R console. You write a function,
submit it, and the package tells you instantly whether it's correct,
with a helpful explanation either way.

No website, no sign-up, no internet connection needed once installed.
Everything runs locally, on your own machine.

This guide walks you through solving your very first challenge, step
by step, assuming you've never used the package before.

## Step 1: Load the package

```{r}
library(rgrind)
```

## Step 2: See what challenges are available

```{r}
list_challenges()
```

Each of these is a short id you can use to try that specific
challenge. Let's start with `sum_evens`. a good first challenge.

## Step 3: Write your own solution

Before submitting anything, you need to write your own R function that
attempts to solve the problem. For `sum_evens`, the goal is: **given a
vector of numbers, add up only the even ones**.

Here's an attempt:

```{r}
my_solution <- function(x) {
  sum(x[x %% 2 == 0])
}
```

This is just a normal R function, written and tested however you'd
normally write R code. `rgrind` doesn't require any special syntax
, any function that takes the right inputs and returns the right
answer will work.

## Step 4: Submit it with `run_challenge()`

```{r}
run_challenge("sum_evens", my_solution)
```

Notice a few things in that output:

- A **green checkmark** and "All tests passed!" means your function
  produced the correct answer for every test case tried against it.
- Right after that, an **Explanation** section shows the idiomatic
  (best-practice) way to solve this exact problem, useful even when
  you passed, since there's often a cleaner or faster approach to
  learn from.
- A **streak** line appears too, more on that in the next guide,
  [Tracking Your Progress](tracking-progress.html).

## Step 5: What happens when you're wrong?

Let's deliberately submit a broken solution, just to see what that
looks like:

```{r}
broken_solution <- function(x) {
  sum(x)  # forgot to filter for even numbers!
}

run_challenge("sum_evens", broken_solution)
```

Instead of a checkmark, you'll see:

- A **red summary line** showing how many test cases passed out of
  the total.
- A **Failed tests** section, showing exactly what was expected versus
  what your function actually returned, for each failing case.
- A **Hint**, a nudge in the right direction, without giving away the
  full answer.

This is completely normal, failing a challenge is part of learning.
Read the hint, adjust your function, and try `run_challenge()` again
with your updated solution.

## Step 6: Try more challenges

Each challenge works exactly the same way: write a function, run
`run_challenge("challenge_id", your_function)`, read the feedback.

```{r}
run_challenge("count_na", function(x) sum(is.na(x)))
```

You can explore every available challenge, along with its category
and difficulty, using `list_challenges()` at any time.

## What's next

Once you're comfortable solving individual challenges, check out the
[Tracking Your Progress](tracking-progress.html) guide to learn about
streaks, your solving history, and the activity heatmap, the parts of
`rgrind` that turn practice into a habit.
