---
title: "Tracking Your Progress"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tracking Your Progress}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(rchallenge.storage_dir = tempfile("vignette_"))
dir.create(getOption("rchallenge.storage_dir"))
```

This guide assumes you've already solved at least one challenge, if
you haven't yet, start with
[Getting Started with rchallenge](getting-started.html) first.

Every time you attempt a challenge, `rchallenge` quietly records it,
locally, on your own machine, in a small file it manages for you.
Nothing is ever sent anywhere. This local history is what powers
streaks, stats, and the activity heatmap.

## Solving something to track

```{r}
library(rchallenge)

run_challenge("sum_evens", function(x) sum(x[x %% 2 == 0], na.rm = TRUE))
```

Notice the line with a flame, that's your **current streak**: the
number of consecutive days (including today) on which you've solved
at least one challenge.

## Understanding streaks

A streak counts **calendar days with at least one passing solve**, not
individual solves. Solving five challenges today still only counts as
one streak day. Solving nothing today doesn't break your streak
immediately either, your streak stays alive until the day *after* the
one you last solved something, giving you until the end of today to
keep it going.

## Checking your overall stats

```{r}
rc_stats()
```

This shows:

- **Challenges solved** : how many distinct challenges you've fully
  passed at least once (out of the total available)
- **Total attempts** : every submission you've made, passing or not
- **Current streak** : your active consecutive-day count
- **Longest streak** : the best run you've ever had, even if it's
  since ended

## Viewing your activity heatmap

```{r}
rc_heatmap()
```

This shows the last 28 days as a simple grid, one row per week. Each
symbol represents how many challenges you passed that day:

- `·` : no solves that day
- `▪` : 1 solve
- `▓` : 2-3 solves
- `█` : 4 or more solves

It's a quick visual way to see your consistency over time — the kind
of thing that's satisfying to watch fill in as you build a habit.

## Viewing your raw history

If you want the full underlying data, every single attempt, with
timestamps, you can access it directly:

```{r}
rc_get_history()
```

This can be useful if you want to analyse your own progress further
(for example, seeing which challenges took you multiple attempts).

## Starting fresh

If you ever want to wipe your local history completely, for example,
if you're demonstrating the package to someone else, or just want a
clean slate, you can reset it:

```r
rc_reset_history()
```

**This cannot be undone**, so use it deliberately.

## What's next

That's the full loop: solve challenges, build a streak, watch your
heatmap fill in. Run `list_challenges()` any time to see what's left
to try, and come back daily to keep your streak alive.
